%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[overlapped, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{6.5in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Adam Duston} % Your name at the top
 
% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{aduston@gmail.com}% Your address
\moveleft.5\hoffset\centerline{312-375-9879}
\moveleft.5\hoffset\centerline{New York City}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{SUMMARY}  

Entrepreneur and software developer who excels at solving problems in a variety of domains. Highly motivated leader and manager.
Substantial experience in distributed systems and information retrieval.

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Co-Founder, VP Product Development} \hfill 2012 - Present \\
Docurated, New York, NY\vspace{2pt}\\
Led projects and teams while contributing significant volume of code. Responsible for the design, development, UX, performance monitoring, and commercial viability of major product components. Instrumental in building company to \$5MM in ARR and eventual acquisition.
\begin{itemize}
\item Developed core search algorithm powering the product, which made novel use of organization activity to rank documents and ensure the most relevant content was surfaced to the user.
\item Led team of four through the design and creation of a commercially successful large-scale ETL and analytics system on Kafka, Spark, GraphX, Redshift, and Tableau, providing customers critical insights on user behavior with content.
\item Led team of four in creation and management of a generalized document synchronization framework and over a dozen third-party document system integrations. Designed and implemented rigorous performance metrics, and defined and hit SLAs for synchronization latency.
\item Designed, developed, and productized automated topic classification system based on a multiclass logistic regression model using bag-of-words features with TF/IDF weighting.
\item Frequently communicated with customers, constantly transmitting customer reality to the engineering team with great enthusiasm.
\item As a generalist engineer on a small team, wrote code that runs across our entire stack, including web-based user interfaces, a desktop sync application, and backend processing systems. Automated provisioning and deployment.
\end{itemize} 

{\sl CTO} \hfill 2010 - 2012 \\
Amara, amara.org
\begin{itemize}
\item Built an award-winning caption and subtitle editor that has been used by The New York Times, Wikipedia, and Mozilla.
\item Led scaling and architecture, and was responsible for all major technology decisions. Coded across entire stack, from user interface to server-side API logic. Automated provisioning and deployment.
\end{itemize}

{\sl CEO} \hfill 2008 - 2010 \\
Langolab
\begin{itemize}
\item Founded and built langolab.com, a site that helped visitors learn foreign languages through subtitled online video.
\item Achieved 3,000 daily unique visitors.
\item Out of approximately 600 applicants, was among the ten selected to participate in TechStars Boston 2009, the inaugural TechStars Boston class.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION} 

University of Chicago \hfill 2003 - 2006 \\
{\sl Economics, Math, and Computer Science}\vspace{2pt}\\
Left school two classes short of a B.A. in Economics to pursue entrepreneurial idea. Relevant coursework includes: Honors Analysis, Honors Algebra, Honors Econometrics, Artificial Intelligence, Compilers, Complexity Theory, Systems Programming, Software Construction.
 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
